1-generate-toys

### 2017-12-06 analysis/analyses/3-score_rules/1-generate-toys.Rmd

qsub_run(
  function(x) {
    library(tidyverse)
    parallel::mclapply(seq_len(nrow(toys)), function(row_id) {
      row <- dynutils::extract_row_to_list(toys, row_id)
      compare_gs_toy(.$gs, .$toy, .$gs_grouped)
    })
  },
  qsub_config = override_qsub_config(num_cores = 24),
  qsub_environment = list2env(list(compare_toy, compare_gs_toy, toys)
)

>>>>

qsub_run(
  function(x) {
    library(tidyverse)
    parallel::mclapply(seq_len(nrow(toys)), function(row_id) {
      row <- dynutils::extract_row_to_list(toys, row_id)
      compare_gs_toy(.$gs, .$toy, .$gs_grouped)
    })
  },
  qsub_config = override_qsub_config(num_cores = 24),
  qsub_environment = list2env(list(compare_toy, compare_gs_toy, toys)
))
